\papertitle

### 2021-03-08 source_separation/paper/paper.tex
Edit intro

	\textit{The following (from here until the line) is directly copy/pasted from our last paper, it will need to be changed in order to avoid self-plagiarism}

	The development of computational tools to assist and inspire the musical composition process constitutes an important research area known as \emph{Computer-Assisted Composition (CAC)} \cite{FerVic2013, Ari2005}. Within CAC, target-based computer-assisted orchestration is a compelling case of how machine learning can be used for {enhancing} and {assisting} music creativity \cite{Maresz2003}.

	 ----------------------------------------------------------

	 \textit{Everything below this line in the introduction is newly written for this paper}

	 In the field of computer-assisted composition, musical orchestration is probably the most empirical one and it has been traditionally taught in an intuitive and non formalized way. Computer-assisted orchestration seeks to help composers by accelerating certain creative processes. In particular, target-based computer-assisted orchestration helps composers explore new timbral possibilities by combining instrumental samples in such a way as to mimic the timbre of a given target sound. Formally, it is the process of creating an orchestral score that best matches an arbitrary target sound given a similarity metric and constraints~\cite{Maresz2003}.

>>>>

	Computer-assisted composition is a field that focuses on the creation of computational tools to aid in the musical composition process \cite{FerVic2013, Ari2005}. Within this field, target-based computer-assisted musical orchestration is an example of how musical creativity can be assisted and supported by tools such as machine learning. Orchestration has been traditionally taught in an intuitive and non formalized way, and computer-assisted orchestration seeks to help composers by accelerating certain creative processes. In particular, target-based computer-assisted orchestration helps composers explore new timbral possibilities by combining instrumental samples in such a way as to mimic the timbre of a given target sound. Formally, it is the process of creating an orchestral score that best matches an arbitrary target sound given a similarity metric and constraints~\cite{Maresz2003}.
